AFQ-Insight

### 2019-12-16 reports/manuscript/sections/introduction.tex
Update reports/manuscript/sections/introduction.tex

Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique
view into the physical properties of the connections that comprise
the brain white matter. While the measurements are usually conducted
with voxels at the millimeter scale, water molecules within each voxel
diffuse with characteristic lengths at the micrometer scale, providing
aggregate information about the physical structure of the white matter,
including the density of axons and distribution of nerve fascicle
orientations within each voxel \cite{wandell2016clarifying}. Even though
metrics derived from diffusion measurements are ambiguous in terms
of their underlying biological interpretation \cite{Jones2013-xv},
analyzing the variance in these properties has proven useful in
characterizing individual differences in cognitive function,
characterizing differences between populations and detecting brain
abnormalities associated with disease \cite{Thomason2011-qn}.

>>>>

Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique
view into the physical properties of the connections that comprise
the brain white matter. While the measurements are usually conducted
with voxels at the millimeter scale, water molecules within each voxel
diffuse with characteristic lengths at the micrometer scale, providing
aggregate information about the physical structure of the white matter,
including the density of axons and distribution of fiber
orientations within each voxel \cite{wandell2016clarifying}. Even though
metrics derived from diffusion measurements are ambiguous in terms
of their underlying biological interpretation \cite{Jones2013-xv},
analyzing the variance in these properties has proven useful in
characterizing individual differences in cognitive function,
characterizing differences between populations and detecting brain
abnormalities associated with disease \cite{Thomason2011-qn}.
